Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-09 mtjournal.tex
minor title tweak
add macros for strikeout
introduction and some limited background

\begin{document}                                                                                   
\begin{article}
\begin{opening}         
\title{Expected Dependency Pair Match:\\
Predicting improvements to {HTER} with expected syntactic structure} 
\author{Jeremy G. \surname{Kahn}\email{jgk@u.washington.edu}}  
\institute{University of Washington}
\author{Matthew \surname{Snover}\email{snover@cs.umd.edu}}
\institute{University of Maryland}
\author{Mari \surname{Ostendorf}\email{ostendor@u.washington.edu}}  
\institute{University of Washington}
\runningauthor{Kahn, Snover \& Ostendorf}
\runningtitle{Expected Dependency Pair Match}
%s\date{May 10, 2009}

@@

\section{Introduction}

\begin{itemize}
\item evaluation [esp. automatic evaluation]
\item popular current
  measures BLEU \cite{papineni02bleu}, TER

\item challenges - motivate search for better measures

\item other extensions:
  \begin{itemize}
  \item METEOR 
    \begin{itemize}
    \item stemming and synonym tables
    \item tuned but not generally     tuneable
    \end{itemize}
  \item TERp
    \begin{itemize}
    \item development-set tuning by user
    \item stemming and synonym tables
    \item paraphrase tables
    \end{itemize}
  \end{itemize}
\item prior work with (partial) syntactic locality:
  \begin{itemize}
  \item Liu \& Gildea 
  \item Roark et al. Sparseval
  \item Owczarzak et al. 2007
  \end{itemize}

>>>>

% package provides \sout{} strikeout macro -- remove this before submission
\usepackage{ulem}

\begin{document}
\begin{article}
\begin{opening}         
\title{Expected Dependency Pair Match:\\
Predicting {HTER} improvements with expected syntactic structure} 
\author{Jeremy G. \surname{Kahn}\email{jgk@u.washington.edu}}  
\institute{University of Washington}
\author{Matthew \surname{Snover}\email{snover@cs.umd.edu}}
\institute{University of Maryland}
\author{Mari \surname{Ostendorf}\email{ostendor@u.washington.edu}}  
\institute{University of Washington}
\runningauthor{Kahn, Snover \& Ostendorf}
\runningtitle{Expected Dependency Pair Match}
%s\date{May 10, 2009}

@@

% override ulem 's default change of \emph{} -- remove before ship
\normalem
\section{Introduction}

\begin{itemize}
\item \sout{ evaluation [esp. automatic evaluation]}
\item \sout{popular current
  measures BLEU \cite{papineni02bleu}, TER}
\end{itemize}
Machine translation (MT) evaluation is a challenge for research
because the space of good translations is large, and two equally good
translations may appear to be quite different at first glance. 
%
The challenges of choosing among translations are compounded when this
evaluation is done automatically.
%
Human evaluation, however, is both time-consuming and difficult, so
research has turned increasingly towards automatic measures of
translation quality, usually by comparing the system translation to
one or more reference (human) translations.
%
Automatic measures of this kind (e.g.\ BLEU \cite{papineni02bleu}) not
only provide a well-defined evaluation standard but are also required
for training on error criteria, e.g.\ with minimum error rate training
\cite{och03mert}.

The most popular evaluation measures are currently BLEU (based on
$n$-gram precision) and the edit-distance measure Translation Edit
Rate (TER) \cite{snover06ter}.  Recent research has found that these
measures may not accurately track translation quality both empirically
\cite{charniak03syntaxlmmt} and theoretically
\cite{callisonburch06bleuproblems}.

\begin{itemize}
\item \sout{challenges - motivate search for better measures}
\item \sout{other extensions:}
  \begin{itemize}
  \item \sout{METEOR }
    \begin{itemize}
    \item \sout{stemming and synonym tables}
    \item \sout{tuned but not generally     tuneable}
    \end{itemize}
  \item \sout{TERp}
    \begin{itemize}
    \item \sout{development-set tuning by user}
    \item \sout{stemming and synonym tables}
    \item \sout{paraphrase tables}
    \end{itemize}
  \end{itemize}
\end{itemize}

These challenges have motivated a search for better measures that
incorporate additional language knowledge sources.  METEOR
\cite{banerjee05meteor}, for example, uses synonym tables and
morphological stemming to do progressively more-forgiving matching.
It can be tuned towards recall or precision, but is generally not
tuned by users.  TERp \cite{snover09terp} is an extension of the
previously-mentioned TER that also incorporates synonym sets, along
with automatically-derived paraphrase tables.  TERp is explicitly
intended to be tuned to a development set by users.

\begin{itemize}
\item prior work with (partial) syntactic locality:
  \begin{itemize}
  \item Liu \& Gildea 
  \item Roark et al. Sparseval
  \item Owczarzak et al. 2007
  \end{itemize}
